### 2021-02-11 abstract.tex
update abstract for submission

In this paper we investigate whether or not the use of static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes. Therefore, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compares dynamic test case generation tools for mining sandboxes, isolating all possible effects of the static analysis, that could leverage the results. We then conducted a new study to investigate the performance of tainted analysis algorithms for mining sandboxes.

>>>>

In this paper we investigate whether or not the use of static analysis might complement and increase the performance of dynamic analysis tools for mining Android sandboxes. Therefore, we first conducted a non-exact replication of a previous study \cite{DBLP:conf/wcre/BaoLL18} that compares dynamic test case generation tools for mining sandboxes, isolating all possible effects on the results of the static analysis tools the original work leverage to instrument the Android apps. We then conducted a new study to investigate the performance of tainted analysis algorithms for mining sandboxes.
